### 2019-02-20 README.Rmd
dropped packrat and moved to checkpoint based package loading

- Intall R and Rstudio.

@@

- Install the required packages using `packrat` as follows.

```{r get-packages, eval = FALSE}
install.packages("packrat")
packrat::restore()

```

>>>>

- Intall R (analysis run with `3.5.0`) and Rstudio.

@@

- Install the required packages using the following script. Versioned to "2018-06-19".

```{r get-packages, eval = FALSE}
source("scripts/packages.R")
```
